\ProjectName{}: Data Imputation as a Query Optimization

### 2017-02-26 paper/algorithm.tex
paper: clarified caption for bad pareto situation (sam feedback)

% arrows
\draw[->] (p1) -- node[right] {$\scriptstyle I$} (p1');
\draw[->] (p2) -- node[right] {$\scriptstyle I$} (p2');
\end{tikzpicture}
\caption{A bad Pareto frontier selection would choose $p_2$ and never reach $p_1'$}
\label{fig:bad-sit-diagram}
\end{figure}

>>>>

% arrows
\draw[->] (p1) -- node[right] {$\scriptstyle I$} (p1');
\draw[->] (p2) -- node[right] {$\scriptstyle I$} (p2');
\end{tikzpicture}
\caption{A bad Pareto frontier selection would choose $p_2$ over $p_1$, as it is locally optimal, but with the available transformations ($I$) $p_2$  can only reach $p_2'$, which is dominated by the inaccessible $p_1'$. Theorem~\ref{theorem:no-bad-sit} says such a situation cannot arise when constructing Pareto frontiers on a dirty-set basis.}
\label{fig:bad-sit-diagram}
\end{figure}
